Demographic consequences of partner diversity and turnover in a multi-species ant-plant mutualism

### 2025-06-18 Manuscript/Previous Version/ant_cactus.tex
Manuscript Updates

\documentclass[11pt]{article}
\usepackage{amsmath}
%\usepackage[sc]{mathpazo} %Like Palatino with extensive math support
\usepackage{fullpage}
\usepackage[authoryear]{natbib}
\linespread{1.7}
\usepackage[utf8]{inputenc}
\usepackage{lineno}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{placeins}
\usepackage{float}
\usepackage{subfigure}
\newcommand{\tom}[2]{{\color{red}{#1}}\footnote{\textit{\color{red}{#2}}}} 
\newcommand{\ali}[2]{{\color{blue}{#1}}\footnote{\textit{\color{blue}{#2}}}}  
\usepackage{hyperref}

@@

\title{Thank you, next: demographic consequences of partner diversity and turnover in a multi-species ant-plant mutualism}
% title suggestion, trying to move away from focus on IPM

\author{Alexandra Campbell$^{1,\dagger}$ \\ 
	Tom E.X. Miller$^{1,\ast}$}

@@

	\noindent{} 1. Program in Ecology and Evolutionary Biology, Department of BioSciences, Rice University, Houston, Texas 77005;

	\noindent{} $\dagger$ e-mail: amc49@rice.edu\\
	\noindent{} $\ast$ e-mail: tom.miller@rice.edu

@@

\section*{Data and Code Availability}
Most of the data that support the findings of this study (through 2019) are openly available as a \href{https://portal.edirepository.org/nis/mapbrowse?packageid=knb-lter-sev.323.1}{data package} \citep{DataCholla} on the Environmental Data Initiative website, package id: knb-lter-sev.323.1.
An updated data package, including recent years, is presently under review and we expect will be available in early 2025. 
For now, all of our data and code are available in our public github repo: \url{https://github.com/acampbell110/ant_cactus_demography}.

>>>>

\documentclass[11pt]{article}
\usepackage{amsmath}
%\usepackage[sc]{mathpazo} %Like Palatino with extensive math support
\usepackage{fullpage}
\usepackage[authoryear,sectionbib,sort]{natbib}
\linespread{1.7}
\usepackage[utf8]{inputenc}
\usepackage{lineno}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{placeins}
\usepackage{float}
\usepackage{subfigure}
\newcommand{\tom}[2]{{\color{red}{#1}}\footnote{\textit{\color{red}{#2}}}} 
\newcommand{\ali}[2]{{\color{blue}{#1}}\footnote{\textit{\color{blue}{#2}}}}  
\usepackage{hyperref}

@@

\title{Demographic consequences of partner diversity and turnover in a multi-species ant-plant mutualism}
% title suggestion, trying to move away from focus on IPM

%\author{Alexandra Campbell$^{1,\dagger}$ \\ 
%	Tom E.X. Miller$^{1,\ast}$}

@@

%	\noindent{} 1. Program in Ecology and Evolutionary Biology, Department of BioSciences, Rice University, Houston, Texas 77005;

%	\noindent{} $\dagger$ e-mail: amc49@rice.edu\\
%	\noindent{} $\ast$ e-mail: tom.miller@rice.edu

@@

\section*{Data and Code Availability}
This section will be filled out once double blind reviews are complete. 
%Most of the data that support the findings of this study (through 2019) are openly available as a \href{https://portal.edirepository.org/nis/mapbrowse?packageid=knb-lter-sev.323.1}{data package} \citep{DataCholla} on the Environmental Data Initiative website, package id: knb-lter-sev.323.1.
%An updated data package, including recent years, is presently under review and we expect will be available in early 2025. 
%For now, all of our data and code are available in our public github repo: \url{https://github.com/acampbell110/ant_cactus_demography}.

### 2025-06-18 Manuscript/References_Cacti.tex
Manuscript Updates

>>>>

@article{Loreau1999,
	title = {Biodiversity and Ecosystem Functioning: Effects of Species Diversity on Productivity and Stability in Plant Communities},
	author = {Loreau, Michel},
	journal = {Proceedings of the Royal Society B: Biological Sciences},
	volume = {264},
	number = {1381},
	pages = {127–130},
	year = {1999},
	doi = {10.1098/rspb.1999.0601}
}
@article{Tilman1994,
	title = {Biodiversity and Stability in Grasslands},
	author = {Tilman, David and Wedin, David and Knops, Johannes},
	journal = {Nature},
	volume = {367},
	pages = {363–365},
	year = {1994},
	doi = {10.1038/367363a0}
}
@article{Hautier2014,
	title = {Eutrophication weakens stabilizing effects of diversity in natural grasslands},
	author = {Hautier, Yann and Isbell, Forest and Borer, Elizabeth T. and Seabloom, Eric W. and Harpole, William S. and Lind, Eric M. and MacDougall, Andrew S. and Stevens, Carly J. and Tilman, David},
	journal = {Nature},
	volume = {508},
	pages = {521–525},
	year = {2014},
	doi = {10.1038/nature13014}
}
